---
title: "Resultados"
author: "Cícero"
date: "2022-09-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Variáveis testadas:

SalePrice x LotArea : Significativa

SalePrice x ExterQual : Siginificativa

SalePrice x ExterCond : significativa

SalePrice x OverallCond : Meio meh

SalePrice x Neighborhood : significativa para algumas vizinhaças

SalePrice x TotalBsmtSF : significativa

SalePrice x MiscVal : Poha nenhuma

SalePrice x MiscFeature : Poha nenhuma

```{r modelo}
dados <- read.csv('train.csv')
modeloLotArea <- lm(SalePrice ~ LotArea,dados)
summary(modeloLotArea)

modeloExterQual <- lm(SalePrice ~ ExterQual,dados)
summary(modeloExterQual)

modeloExterCond <- lm(SalePrice ~ ExterCond,dados)
summary(modeloExterCond)

modeloOverallCond <- lm(SalePrice ~ OverallCond,dados)
summary(modeloOverallCond)

modeloNeighborhood <- lm(SalePrice ~ Neighborhood,dados) 
summary(modeloNeighborhood)

modeloTotalBsmtSF <- lm(SalePrice ~ TotalBsmtSF,dados)
summary(modeloTotalBsmtSF)

modeloMiscVal <- lm(SalePrice ~ MiscVal,dados)
summary(modeloMiscVal)

modeloMiscFeature <- lm(SalePrice ~ MiscFeature,dados)
summary(modeloMiscFeature)

```



## Lm Plots


````{r pressure, echo=FALSE}

abline(plot(with(dados,lm(SalePrice ~ LotArea))))

abline(plot(with(dados, lm(SalePrice ~ ExterQual))))

abline(plot(with(dados,lm(SalePrice ~ OverallCond))))

abline(plot(with(dados, lm(SalePrice ~ Neighborhood))))

abline(plot(with(dados, lm(SalePrice ~ TotalBsmtSF))))



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
